---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# safejoin

<!-- badges: start -->
[![R build status](https://github.com/SamEdwardes/safejoin/workflows/R-CMD-check/badge.svg)](https://github.com/SamEdwardes/safejoin/actions)
<!-- badges: end -->

The goal of safejoin is to guarantee that when performing joins that extra rows are not added to your data. safejoin is a wrapper around the [`dplyr::left_join`](https://dplyr.tidyverse.org/reference/join.html) function.

- [Docs](https://safejoin-r.netlify.app/)
- [GitHub](https://github.com/SamEdwardes/safejoin/)
- CRAN (not yet published)

## Installation

safejoin is currently under development. An update will be published here once the package is published on CRAN.

<!--
You can install the released version of safejoin from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("safejoin")
```
-->

## Example

Depending on your need safejoin can raise an error, a warning, or a message. By default safejoin will raise an error.

**Error**:

```{r example, error=TRUE}
library(safejoin)
x <- data.frame(key = c("a", "b"), value_x = c(1, 2))
y <- data.frame(key = c("a", "a"), value_y = c(1, 1))
safe_left_join(x, y, by = "key")
```

**Warning**:

```{r example_warning}
safe_left_join(x, y, by = "key", action="warning")
```

**Message**:

```{r example_message}
safe_left_join(x, y, by = "key", action="message")
```

When a join is "safe" `safe_left_join` will have the exact same behavior as [`dplyr::left_join`](https://dplyr.tidyverse.org/reference/join.html).

```{r}
x <- data.frame(key = c("a", "b"), value_x = c(1, 2))
y <- data.frame(key = c("a", "b"), value_y = c(1, 1))
safe_left_join(x, y, by = "key")
```

