---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# safejoin

The goal of safejoin is to guarantee that when performing joins that extra rows are not added to your data.

## Installation

You can install the released version of safejoin from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("safejoin")
```

## Example

Depending on your need safejoin can throw an error, a warning, or a message. By default safejoin will throw an error.

**Throwing an error**:

```{r example, error=TRUE}
library(safejoin)
x <- data.frame(key = c("a", "b"), value_x = c(1, 2))
y <- data.frame(key = c("a", "a"), value_y = c(1, 1))
safe_left_join(x, y, by = "key")
```

**Throwing a warning**:

```{r example_warning}
safe_left_join(x, y, by = "key", action="warning")
```

**Throwing a message**:

```{r example_message}
safe_left_join(x, y, by = "key", action="message")
```

